Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-05-26 paper.tex
Adds discussion of create/delete overhead results Fixes labeling issue for figures

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{framed}
\usepackage{floatrow}
\usepackage{comment}

@@

@@

Availability of the experiment is an important consideration for reproducibility. We have provided the source code, which is freely available on GitHub at {\tt{https://github.com/cooperative-computing-lab/disk-alloc-experiment}}. Within this git repository we have included the data collected for this technical report and a convenient Makefile which makes running the experiment quite simple. This Makefile downloads all the dependent code for the experiment except some software listed in the {\tt{README}} located in the repository as well as runs the specified tests, generates graphs from the test data, and compiles this paper. We chose to provide this depth of content because reproducibility and availability are high priorities with respect to this technical report.

@@

\begin{figure*}[t]
\begin{tabular}{ccc}
ext2 & \cimage{./previous_results/create_ext2.pdf} & \cimage{./previous_results/delete_ext2.pdf}\\
ext3 & \cimage{./previous_results/create_ext3.pdf} & \cimage{./previous_results/delete_ext3.pdf}\\
ext4 & \cimage{./previous_results/create_ext4.pdf} & \cimage{./previous_results/delete_ext4.pdf}\\
\end{tabular}
\label{fig:create}
\caption{Loop Device Creation/Deletion Overhead}
\end{figure*}

\newpage
\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_2GB.pdf} & \cimage{./previous_results/write_ext2_2GB.pdf} & \cimage{./previous_results/meta_ext2_2GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_2GB.pdf} & \cimage{./previous_results/write_ext3_2GB.pdf} & \cimage{./previous_results/meta_ext3_2GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_2GB.pdf} & \cimage{./previous_results/write_ext4_2GB.pdf} & \cimage{./previous_results/meta_ext4_2GB.pdf}\\
\end{tabular}
\label{fig:2gb}
\caption{Loop Device Performance with 2GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_4GB.pdf} & \cimage{./previous_results/write_ext2_4GB.pdf} & \cimage{./previous_results/meta_ext2_4GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_4GB.pdf} & \cimage{./previous_results/write_ext3_4GB.pdf} & \cimage{./previous_results/meta_ext3_4GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_4GB.pdf} & \cimage{./previous_results/write_ext4_4GB.pdf} & \cimage{./previous_results/meta_ext4_4GB.pdf}\\
\end{tabular}
\label{fig:4gb}
\caption{Loop Device Performance with 4GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_8GB.pdf} & \cimage{./previous_results/write_ext2_8GB.pdf} & \cimage{./previous_results/meta_ext2_8GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_8GB.pdf} & \cimage{./previous_results/write_ext3_8GB.pdf} & \cimage{./previous_results/meta_ext3_8GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_8GB.pdf} & \cimage{./previous_results/write_ext4_8GB.pdf} & \cimage{./previous_results/meta_ext4_8GB.pdf}\\
\end{tabular}
\label{fig:8gb}
\caption{Loop Device Performance with 8GB Allocations}
\end{figure*}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{framed}
\usepackage{floatrow}
\usepackage{comment}
\usepackage{hyperref}

@@

The results presented in Figure \ref{fig:create} display the median value of each sandbox size's creation time. Like in the throughput performance results, we have provided the median absolute deviation for each sandbox size. We can see a proportional linear increase in creation time as the sandbox size increases which is expected. The smaller sandbox sizes (< 1GB) take very little time to instantiate with 512MB taking approximately six seconds to set up. This small overhead should have minimal impact upon performance except in cases where the task would run in a matter of a few seconds where the overhead for instantiating a loop device could double the duration of a task. Considering larger allocations, we see that the overhead is still quite reasonable. 1GB sandboxes across all three ext filesystems show a creation overhead of approximately eleven seconds. On the high end of our testing spectrum, we see an 8GB allocation having a seventy second instantiation duration. In normal cases, we notice that allocations of 8GB or greater experience computation on the order of tens of minutes or longer, so the creation overhead does not seem to dominate a task's duration. In certain cases, however, only a small fraction of the data passed into the sandbox will be relevant to computation. In this case, the creation overhead may be as great as the time spent on computation. We note that file transfer for the data would dominate a task's duration in this case and not the loop device instantiation.

Loop device deletion seems to be almost trivial in duration. In our implementation, the sandbox is dereferenced once the task is complete. In the future, we may opt to overwrite the disk space consumed by the sandbox with zeros before dereferencing the pointers to the disk, however this was not a priority in the current implementation. In all instances of our deletion overhead testing, we can see that the time taken to remove a loop device is less than half a second. As is expected, the 8GB allocation took the longest to remove. In the lower end of our testing spectrum, we note that the smallest allocations took longer to remove than the mid-range allocation sizes in ext3 and ext4. We posit this may be due to handling within ext3 and ext4 which derefences very small files in a less efficient manner with a neglibgible performance decrease compared to a more advanced handling mechanism for larger files. The largest difference we observe is approximately 0.05 seconds between a 16MB and a 32MB allocation which is a speed no human user would likely notice.

@@

Availability of the experiment is an important consideration for reproducibility. We have provided the source code, which is freely available on GitHub at {\url{https://github.com/cooperative-computing-lab/disk-alloc-experiment}}. Within this git repository we have included the data collected for this technical report and a convenient Makefile which makes running the experiment quite simple. This Makefile downloads all the dependent code for the experiment except some software listed in the {\tt{README}} located in the repository as well as runs the specified tests, generates graphs from the test data, and compiles this paper. We chose to provide this depth of content because reproducibility and availability are high priorities with respect to this technical report.

@@

\begin{figure*}[t]
\begin{tabular}{ccc}
ext2 & \cimage{./previous_results/create_ext2.pdf} & \cimage{./previous_results/delete_ext2.pdf}\\
ext3 & \cimage{./previous_results/create_ext3.pdf} & \cimage{./previous_results/delete_ext3.pdf}\\
ext4 & \cimage{./previous_results/create_ext4.pdf} & \cimage{./previous_results/delete_ext4.pdf}\\
\end{tabular}
\caption{Loop Device Creation/Deletion Overhead}
\label{fig:create}
\end{figure*}

\newpage
\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_2GB.pdf} & \cimage{./previous_results/write_ext2_2GB.pdf} & \cimage{./previous_results/meta_ext2_2GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_2GB.pdf} & \cimage{./previous_results/write_ext3_2GB.pdf} & \cimage{./previous_results/meta_ext3_2GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_2GB.pdf} & \cimage{./previous_results/write_ext4_2GB.pdf} & \cimage{./previous_results/meta_ext4_2GB.pdf}\\
\end{tabular}
\caption{Loop Device Performance with 2GB Allocations}
\label{fig:2gb}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_4GB.pdf} & \cimage{./previous_results/write_ext2_4GB.pdf} & \cimage{./previous_results/meta_ext2_4GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_4GB.pdf} & \cimage{./previous_results/write_ext3_4GB.pdf} & \cimage{./previous_results/meta_ext3_4GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_4GB.pdf} & \cimage{./previous_results/write_ext4_4GB.pdf} & \cimage{./previous_results/meta_ext4_4GB.pdf}\\
\end{tabular}
\caption{Loop Device Performance with 4GB Allocations}
\label{fig:4gb}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{./previous_results/read_ext2_8GB.pdf} & \cimage{./previous_results/write_ext2_8GB.pdf} & \cimage{./previous_results/meta_ext2_8GB.pdf}\\
ext3 & \cimage{./previous_results/read_ext3_8GB.pdf} & \cimage{./previous_results/write_ext3_8GB.pdf} & \cimage{./previous_results/meta_ext3_8GB.pdf}\\
ext4 & \cimage{./previous_results/read_ext4_8GB.pdf} & \cimage{./previous_results/write_ext4_8GB.pdf} & \cimage{./previous_results/meta_ext4_8GB.pdf}\\
\end{tabular}
\caption{Loop Device Performance with 8GB Allocations}
\label{fig:8gb}
\end{figure*}
